\documentclass[10pt]{article}
\usepackage{graphicx} % Required for inserting images
\usepackage{url}
\usepackage{hyperref}
\title{}
\author{martavictoriaperez }
\date{February 2026}

\usepackage[margin=1in]{geometry} 
\usepackage{amsmath,amsthm,amssymb, graphicx, multicol, array}
 
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
 
\newenvironment{problem}[2][Problem]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}

\begin{document}
 
\title{\textbf{Rubric for grading Course Project}}
\author{
%Your name\\
DTU Course 46770: Integrated Energy Grids }
\maketitle

\begin{itemize}

\item[0.5 points] Proper discussion of optimal capacity/generation mix including plots for the dispatch for one week in summer and winter, annual electricity mix and duration curves. 

\item[0.5 points] Proper discussion of the optimum capacity mix vs global CO2 constraint.

\item[1 point] Proper discussion on interannual sensitivity including plots for average capacities (obtained for different weather years) and interannual variability.
(0.5 points if average and variability are calculated + 0.5 points if the reasoning of differences among technologies is provided)

\item[1 point] Proper discussion on storage technologies and how they modify the optimal capacity mix.


\item[1 point] 0.5 points for the description and implementation of the interconnected model + 0.5 points for reasoning on the impacts of the interconnected model compared to a single node. 

\item[1 point] 0.5 points for the correct calculation of the incidence matrix and the power transfer distribution factor (PTDF) matrix of the network + 0.5 points for the correct calculation of the optimal power flowing through every line.

\item[1 point] 0.5 points for the description and implementation of the gas network + 0.5 points for the comparison of energy transported by both types of networks

\item[0.5 points] Calculation of CO$_2$ price and reporting on currently existing CO$_2$ price, including the comparison between them and reasoning

\item[1.5 points]  0.5 points for the description of the sector-coupling approach selected + 0.5 points for the model implementation + 0.5 points for reasoning on the impacts of the sector-coupled model compared to the single node.

\item[1 point] 0.5 points for the research question identified + 0.5 points for a description of the modelling approach to investigate it. 

\item[1 point] The text is clear and well structured, figures can be easily read and include proper captions and units.

\end{itemize}


\end{document}


 

